\section*{Selected Peer-Reviewed Publications}

\subsection*{Published or In Press}

% \subsubsection*{2024}

%     \item PAPER

% \begin{itemize}
%     \item XX
%     \item XX
% \end{itemize}

\begin{enumerate}

% 	TBC
    \item \noindent Lynch VD, Sullivan JA, Flores AB, Xie X, Aggarwal S, Nethery RC, Kioumourtzoglou MA, Nigra AE, \textbf{Parks RM}. (2025). Large floods drive changes in cause-specific mortality in the United States. \textbf{Nature Medicine}.\href{https://www.nature.com/articles/s41591-024-03358-z}{ (link)}

    \begin{itemize}
        \item Senior author publication in a high impact journal.
    \end{itemize}

% XX
     \item \noindent Do V, \textbf{Parks RM}, Casey JA,  Goin DE, Kioumourtzoglou MA. (2024). Use, limitations, and future directions of mixtures approaches to understand the health impacts of weather- and climate change-related exposures, an under-studied aspect of the exposome \textbf{Exposome}. \href{https://academic.oup.com/exposome/advance-article/doi/10.1093/exposome/osae007/7824058}{(link)}

    \begin{itemize}
        \item Contributed to manuscript writing.
    \end{itemize}

% 	Recent and Projected Changes in Global Climate May Increase Nicotine Absorption and the Risk of Green Tobacco Sickness, Communications Medicine
    \item \noindent Ziska L, \textbf{Parks RM}. (2024). Recent and projected changes in global climate may increase nicotine absorption and the risk of green tobacco sickness. \textbf{Communications Medicine}.\href{https://www.nature.com/articles/s43856-024-00584-x}{ (link)}

    \begin{itemize}
        \item Senior author publication.
    \end{itemize}
    
% Daily temperature variability and mental health-related hospital visits in New York State
    \item \noindent Cohen G, Rowland ST, Benavides J, Lindert J, Kioumourtzoglou MA, \textbf{Parks RM}. (2024). Daily temperature variability and mental health-related hospital visits in New York State. \textbf{Environmental Research}.\href{https://www.sciencedirect.com/science/article/abs/pii/S0013935124011435}{ (link)}
    
    \begin{itemize}
        \item Senior author publication.
    \end{itemize}

% Climate Change And New York City’s Health Risk, New York City Panel on Climate Change 4th Assessment
    \item \noindent Matte T, Lane K, Tipaldo J, Barnes J, Knowlton K, Torem E, Anand G, Yoon L, Marcotullio P, Balk D, Constible J, Elszasz H, Ito K, Jessel S, Limaye V, \textbf{Parks RM}, Rutigliano M, Sorenson C, Yuan A. (2024). Climate Change And New York City’s Health Risk. \textbf{New York City Panel on Climate Change 4th Assessment}.\href{https://nyaspubs.onlinelibrary.wiley.com/doi/full/10.1111/nyas.15115}{ (link)}

    \begin{itemize}
        \item Co-author on report for NYC's independent advisory body that synthesizes scientific information on climate change to inform City policy.
    \end{itemize}
    
% Climate change and health: Understanding mechanisms will inform mitigation and prevention strategies, Nature Medicine
    \item \noindent Prada D, Kupsco A, Baccarelli AA, \textbf{Parks RM}. (2024). Climate change and health: Understanding mechanisms will inform mitigation and prevention strategies. \textbf{Nature Medicine}.\href{https://www.nature.com/articles/s41591-024-02925-8}{ (link)}

    \begin{itemize}
        \item Senior author publication in a high impact journal.
    \end{itemize}

% The Global Health Community At International Climate Change Negotiations
    \item van Daalen KR, Wyma N, Schauer-Berg J, Blom IM, Mattijsen J, Othman R, Eissa MM, \textbf{Parks RM}, Wyns A, Aboushady ATA, Hassan M, Ezzine T, Khan S, Zayed MAE, Neggazi S, Alqodmani L, Lowe R. (2024). The Global Health Community At International Climate Change Negotiations. \textbf{BMJ Global Health}.\href{https://gh.bmj.com/content/9/4/e015292}{ (link)}

    \begin{itemize}
        \item Contributed to work directly relevant to climate change and health policy for global governance.
    \end{itemize}

% Reflections from COP28: Resisting healthwashing in climate change negotiations, PLOS Global Public Health
    \item Singh A, Ezzine T, Guinto RR, Gepp S, \textbf{Parks RM}, Thondoo M, Patil P, van Daalen KR. (2024). Reflections from COP28: Resisting healthwashing in climate change negotiations. \textbf{PLOS Global Public Health}.\href{https://journals.PLOS.org/globalpublichealth/article?id=10.1371/journal.pgph.0003076}{ (link)}

    \begin{itemize}
        \item Contributed to work directly relevant to climate change and health policy for global governance.
    \end{itemize}

% Hazardous heat exposure among incarcerated people in the United States, Nature Sustainability
    \item Tuholske C, Lynch VD, Spriggs R, Ahn Y, Raymond C, Nigra AE, \textbf{Parks RM}. (2024). Hazardous heat exposure among incarcerated people in the United States. \textbf{Nature Sustainability}.\href{https://www.nature.com/articles/s41893-024-01293-y}{ (link)}

    \begin{itemize}
        \item Senior author publication in a high impact journal.
            \item Coverage of publication by Nina Lakhani on front page of The Guardian website \href{https://www.theguardian.com/us-news/2024/mar/05/prisons-heat-deaths-texas-florida}{(link)}.
            \item Led to contributing to United States Senator Ed Markey's Environmental Health in Prisons Act. 
    \end{itemize}

% Comparing Approximated Heat Stress Measures Across the United States, GeoHealth
    \item \noindent Ahn Y, Tuholske C*, \textbf{Parks RM}*. (2024). Comparing Approximated Heat Stress Measures Across the United States. \textbf{GeoHealth}.\href{https://agupubs.onlinelibrary.wiley.com/doi/10.1029/2023GH000923}{ (link)}

\begin{itemize}
    \item Senior author publication in a specialist journal.
\end{itemize}

\newpage

% \subsubsection*{2023}

% Fifth National Climate Assessment
    \item USGCRP, 2023: Fifth National Climate Assessment. Crimmins, A.R., C.W. Avery, D.R. Easterling, K.E. Kunkel, B.C. Stewart, and T.K. Maycock, Eds. U.S. Global Change Research Program, Washington, DC, USA. \href{https://nca2023.globalchange.gov/chapter/14/}{(link)}

    \begin{itemize}
        \item Technical Contributor to Chapter 14: Air Quality.
        \item Results commissioned by US Congress and used in federal climate change policy.
    \end{itemize}

% The association between temperature and alcohol- and substance-related disorder hospital visits in New York State. Communications Medicine
    \item \noindent \textbf{Parks RM}, Rowland ST, Do V, Boehme AK, Dominici F, Hart CL, Kioumourtzoglou MA. (2023). The association between temperature and alcohol- and substance-related disorder hospital visits in New York State. \textbf{Communications Medicine}. \href{https://www.nature.com/articles/s43856-023-00346-1}{(link)}

\begin{itemize}
    \item First author publication.
    \item Featured publication on journal website.
    \item Media coverage included Grist, KCBS Radio (San Francisco), Global Heat Health Digest.
\end{itemize}

% Short-term excess mortality following tropical cyclones in the United States, Science Advances
    \item \textbf{Parks RM}, Kontis V, Anderson GB, Baldwin JW, Danaei G, Toumi R, Dominici F, Ezzati M, Kioumourtzoglou MA. (2023). Short-term excess mortality following tropical cyclones in the United States. \textbf{Science Advances}. \href{https://www.science.org/doi/10.1126/sciadv.adg6633}{(link)} 

    \begin{itemize}
        \item First author publication in a high impact journal.
        \item Chosen for cover art of journal August 2023 issue \href{https://www.science.org/toc/sciadv/9/33}{(link)}.
        \item Media coverage included The Guardian, NBC News, AP News, The Washington Post, NPR WNYC.
    \end{itemize}

% Exploring Relevant Time Windows in the Association Between PM2.5 Exposure and Amyotrophic Lateral Sclerosis: A Case-Control Study in Denmark
    \item Nunez Y, Balalian A, \textbf{Parks RM}, He M, Hansen J, Raaschou-Nielsen O, Ketzel M, Khan J, Brandt J, Vermeulen R, Peters S, Goldsmith J, Re DB, Weisskopf MG, Kioumourtzoglou MA. (2023). Exploring Relevant Time Windows in the Association Between PM2.5 Exposure and Amyotrophic Lateral Sclerosis: A Case-Control Study in Denmark. \textbf{American Journal of Epidemiology}. \href{https://academic.oup.com/aje/advance-article-abstract/doi/10.1093/aje/kwad099/7135818?redirectedFrom=fulltext&login=false}{(link)}

    \begin{itemize}
        \item Contributed to data processing and modelling.
    \end{itemize}

% Excess Injury Mortality in Washington State During the 2021 Heat Wave, American Journal of Public Health
     \item \noindent Casey JA, \textbf{Parks RM}, Bruckner T, Gemmill A, Catalano R. (2023). Excess Injury Mortality in Washington State During the 2021 Heat Wave. \textbf{American Journal of Public Health}. \href{https://ajph.aphapublications.org/doi/abs/10.2105/AJPH.2023.307269}{(link)}

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
    \end{itemize}

% Assessment of COVID-19 as the Underlying Cause of Death Among Children and Young People Aged 0 to 19 Years in the US, JAMA Network Open
    \item Flaxman S, Whittaker C, Semenova E, Rashid T, \textbf{Parks RM}, Blenkinsop A, Unwin HJT, Mishra S, Bhatt S, Gurdasani D, Ratmann O. (2023). Assessment of COVID-19 as the Underlying Cause of Death Among Children and Young People Aged 0 to 19 Years in the US. \textbf{JAMA Network Open}. \href{https://jamanetwork.com/journals/jamanetworkopen/fullarticle/2800816}{(link)}

    \begin{itemize}
        \item Contributed to data processing, interpretation, and manuscript writing.
    \end{itemize}
% \subsubsection*{2022}

% Invited Perspective: Uncovering the Hidden Burden of Tropical Cyclones on Public Health Locally and Worldwide, EHP
    \item \textbf{Parks RM}, Guinto RR. (2022). Invited Perspective: Uncovering the Hidden Burden of Tropical Cyclones on Public Health Locally and Worldwide. \textbf{Environmental Health Perspectives}. \href{https://ehp.niehs.nih.gov/doi/10.1289/EHP12241}{(link)} 

    \begin{itemize}
    \item First author publication.
        \item EHP Editors' choice for 2022 \href{https://ehp.niehs.nih.gov/curated-collections/eds-choice-2022}{(link)}.
    \end{itemize}

% Estimates of excess mortality for the five Nordic countries during the COVID-19 pandemic 2020-2021, International Journal of Epidemiology
     \item Kepp KP, Bjork JP, Kontis V, \textbf{Parks RM}, Baek KT, Lallukka T. (2022). Estimates of excess mortality for the five Nordic countries during the COVID-19 pandemic 2020-2021, \textbf{International Journal of Epidemiology} \href{https://academic.oup.com/ije/advance-article/doi/10.1093/ije/dyac204/6798817#379089278}{(link)}

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
    \end{itemize}

% Long-term traffic-related air pollutant exposure and amyotrophic lateral sclerosis diagnosis in Denmark: A Bayesian hierarchical analysis, Epidemiology
     \item \textbf{Parks RM}, Nunez Y, Balalian A,  Gibson EA, Hansen J, Raaschou-Nielsen O, Ketzel M, Khan J, Brandt J, Vermeulen R, Peters S, Goldsmith J, Re DB, Weisskopf MG, Kioumourtzoglou MA. (2022). Long-term traffic-related air pollutant exposure and amyotrophic lateral sclerosis diagnosis in Denmark: A Bayesian hierarchical analysis. \textbf{Epidemiology}. \href{https://journals.lww.com/epidem/Abstract/9900/Long_term_traffic_related_air_pollutant_exposure.55.aspx}{(link)}

\begin{itemize}
    \item First author publication.
\end{itemize}

% Ambient temperature and risk of urinary tract infection in California: A time-stratified case-crossover study using electronic health records, Environment International 
    \item Elser H,* Rowland ST,* Tartof SY, \textbf{Parks RM}, Bruxvoort K, Morello-Frosch R, Robinson SC, Pressman A, Wei RX, Casey JA (2022). Ambient temperature and risk of urinary tract infection in California: A time-stratified case-crossover study using electronic health records. \textbf{Environment International} \href{https://www.sciencedirect.com/science/article/pii/S0160412022002306}{(link)}

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
    \end{itemize}

\newpage

% Association of Tropical Cyclones With County-Level Mortality in the US, JAMA
     \item \textbf{Parks RM}, Benavides J, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Ezzati M, Kioumourtzoglou MA. (2022). Association of Tropical Cyclones With County-Level Mortality in the US. \textbf{JAMA} \href{https://jamanetwork.com/journals/jama/fullarticle/2789661}{(link)} 

    \begin{itemize}
        \item First author publication in a high impact journal
        \item 2022 NIEHS Papers of the Year. 
        \item Chosen for editorial comment by James M. Shultz, Lori Peek, Sandro Galea \href{https://jamanetwork.com/journals/jama/fullarticle/2789676}{(link)}.
        \item Media coverage included USA Today, AP News, NBC News, The Hill.
    \end{itemize}

% Lessons learned and lessons missed: Impact of the Covid-19 pandemic on all-cause mortality in 40 industrialised countries prior to mass vaccination, Wellcome Open Research
    \item Kontis V, Bennett JE, \textbf{Parks RM}, Rashid T, Pearson-Stuttard J, Asaria P, Zhou B, Guillot M, Mathers CD, Khang Y, McKee M, Ezzati M. (2022). Lessons learned and lessons missed: Impact of the Covid-19 pandemic on all-cause mortality in 40 industrialised countries prior to mass vaccination, \textbf{Wellcome Open Research} \href{https://wellcomeopenresearch.org/articles/6-279/v2}{(link)}

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
        \item Designed data processing pipeline for temperature records from ERA5 to go into Bayesian ensemble.
    \end{itemize}

% \section*{Selected Publications (Continued)}

% \subsubsection*{2021}

% Causal predictive models for forecasting health impacts of impending tropical cyclones, Biostatistics 
     \item Nethery RC, Katz-Christy N, Kioumourtzoglou MA, \textbf{Parks RM}, Schumacher A, Anderson GB. (2021). Causal predictive models for forecasting health impacts of impending tropical cyclones, \textbf{Biostatistics} \href{https://academic.oup.com/biostatistics/advance-article/doi/10.1093/biostatistics/kxab047/6485226?guestAccessKey=378fb8f6-102d-4b21-a93d-b0a01353c19f#}{(link)}

    \begin{itemize}
        \item Contributed to interpretation of results and manuscript writing.
    \end{itemize}

% Heat vulnerability in New York City during COVID-19: A review of policies, tools and pilot survey results, Journal of Extreme Events
    \item Bock J, Srivastava P, Jessel S, Klopp JM, \textbf{Parks RM}. (2021). Heat vulnerability in New York City during COVID-19: A review of policies, tools and pilot survey results, \textbf{Journal of Extreme Events} \href{https://www.worldscientific.com/doi/10.1142/S2345737621500159}{(link)}

    \begin{itemize}
        \item Senior author publication.
        \item Collaborated with Sonal Jessel of WE ACT for Environmental Justice to produce survey and results.
    \end{itemize}

% Compound risks and complex emergencies require new approaches to preparedness, PNAS
    \item Kruczkiewicz A, Klopp J, Fisher J, Mason S, McClain S, Sheekh NM, Moss R, \textbf{Parks RM}, Braneon C. (2021).\\Compound risks and complex emergencies require new approaches to preparedness, \textbf{PNAS} \href{https://www.pnas.org/content/118/19/e2106795118}{(link)} 

    \begin{itemize}
        \item Contributed to manuscript writing.
    \end{itemize}

% The Association Between Ambient Temperature Variability and Myocardial Infarction: An Examination of Different Variability Metrics, Environmental Research
    \item Rowland S, \textbf{Parks RM}, Boehme AK, Goldsmith J, Rush J, Just AC, Kioumourtzoglou MA. (2021). The Association Between Ambient Temperature Variability and Myocardial Infarction: An Examination of Different Variability Metrics, \textbf{Environmental Research} \href{https://www.sciencedirect.com/science/article/pii/S0013935121005016}{(link)}

    \begin{itemize}
        \item Contributed to code review and manuscript writing.
    \end{itemize}


% Anomalously warm weather and acute care visits in patients with multiple sclerosis: A retrospective study of privately insured individuals in the U.S., PLOS Medicine
     \item Elser H, \textbf{Parks RM}, Moghavem N, Bozinov B, Henderson VW, Rehkopf DH, Casey JA. (2021). Anomalously warm weather and acute care visits in patients with multiple sclerosis: A retrospective study of privately insured individuals in the U.S., \textbf{PLOS Medicine} \href{https://journals.PLOS.org/PLOSmedicine/article?id=10.1371/journal.pmed.1003580}{(link)} 

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
    \end{itemize}

% Tropical cyclone exposure is associated with increased hospitalization rates in older adults, Nature Communications
     \item \textbf{Parks RM}, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Kioumourtzoglou MA. (2021). Tropical cyclone exposure is associated with increased hospitalization rates in older adults, \textbf{Nature Communications} \href{https://www.nature.com/articles/s41467-021-21777-1}{(link)}

    \begin{itemize}
        \item First author publication in a high impact journal.
        \item 2021 NIEHS Papers of the Year. 
    \end{itemize}

% Nationwide Study of Short-Term Exposure to Fine Particulate Matter and Cardiovascular Hospitalizations among Medicaid Enrollees, Epidemiology 
    \item deSouza P, Braun D, \textbf{Parks RM}, Schwartz J, Dominici F, Kioumourtzoglou MA. (2021). Nationwide Study of Short-Term Exposure to Fine Particulate Matter and Cardiovascular Hospitalizations among Medicaid Enrollees, \textbf{Epidemiology} \href{https://journals.lww.com/epidem/Abstract/2021/01000/Nationwide_Study_of_Short_term_Exposure_to_Fine.2.aspx}{(link)}

    \begin{itemize}
        \item Contributed to code review, modelling, and manuscript writing.
    \end{itemize}

% \subsubsection*{2020}

% Magnitude, demographics and dynamics of the effect of the first wave of the COVID-19 pandemic on all-cause mortality in 21 industrialized countries, Nature Medicine
     \item Kontis V, Bennett JE, Rashid T, \textbf{Parks RM}, Pearson-Stuttard J, Guillot M, Asaria P, Zhou B, Battaglini M, Corsetti G, McKee M, Di Cesare M, Mathers C, Ezzati M. (2020). Magnitude, demographics and dynamics of the effect of the first wave of the COVID-19 pandemic on all-cause mortality in 21 industrialized countries, \textbf{Nature Medicine} \href{https://doi.org/10.1038/s41591-020-1112-0}{(link)}

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
        \item Designed data processing pipeline for temperature records from ERA5 to go into Bayesian ensemble.
        \item Worked with international team of collaborators at great speed to generate timely results.
    \end{itemize}

\newpage

% The hidden burden of pandemics, climate change and migration on mental health, UN International Organization for Migration (IOM) thematic series on health
    \item \textbf{Parks RM}, Thalheimer L. (2020). The hidden burden of pandemics, climate change and migration on mental health, \textbf{UN International Organization for Migration (IOM) thematic series on health} \href{https://environmentalmigration.iom.int/blogs/hidden-burden-pandemics-climate-change-and-migration-mental-health}{(link)} 

    \begin{itemize}
        \item First author publication.
    \end{itemize}

% Age- and sex-specific total mortality impacts of the early weeks of the Covid-19 pandemic in England and Wales: Application of a Bayesian model ensemble to mortality statistics, MedrXiv
    \item Kontis V, Bennett JE, \textbf{Parks RM}, Rashid T, Pearson-Stuttard J, Asaria P, Guillot M, Blangiardo M, Ezzati M. (2020). Age- and sex-specific total mortality impacts of the early weeks of the Covid-19 pandemic in England and Wales: Application of a Bayesian model ensemble to mortality statistics, \textbf{MedrXiv} \href{https://www.medrxiv.org/content/10.1101/2020.05.20.20107680v1}{(link)}

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
        \item Designed data processing pipeline for temperature records from ERA5 to go into Bayesian ensemble.
        \item Worked with international team of collaborators at great speed to generate timely results.
    \end{itemize}

% Vital signs: health security in South Africa. Chapter 5: climate, drought, food and health, Brenthurst Foundation, Oppenheimer \& Sons
     \item \textbf{Parks RM}, McLaren M, Rivett U, Thomson M. (2020). Vital signs: health security in South Africa. Chapter 5: climate, drought, food and health, \textbf{Brenthurst Foundation, Oppenheimer \& Sons} \href{https://www.thebrenthurstfoundation.org/downloads/vital-signs-ebook-pdf.pdf}{(link)}

    \begin{itemize}
        \item First author publication.
        \item Collaborated with Madeleine Thomson and collaborators in South Africa.
    \end{itemize}

% (In the top 1\% of all research outputs scored by Altmetric)\\

% Anomalously warm temperatures are associated with increased injury deaths, Nature Medicine
     \item \textbf{Parks RM}, Bennett JE, Tamura-Wicks H, Kontis V, Toumi R, Ezzati M. (2020). Anomalously warm temperatures are associated with increased injury deaths, \textbf{Nature Medicine} \href{https://www.nature.com/articles/s41591-019-0721-y}{(link)} 

    \begin{itemize}
        \item First author publication in a high impact journal
        \item Chosen for editorial comment by Shanthi Ameratunga and Alistair Woodward  \href{https://www.nature.com/articles/s41591-019-0728-4}{(editorial)}.
        \item Media coverage included CNN, The Guardian, TIME.
    \end{itemize}

% % HEADER 
% \input{sections/header}

% \section*{Selected Publications (Continued)}

% \subsubsection*{2019}

% National and county life expectancy loss associated with particulate matter pollution in the USA: a spatiotemporal analysis, PLOS Medicine
\item Bennett JE*, Tamura-Wicks H*, \textbf{Parks RM}, Burnett RT, Pope CA III, Bechle MJ, Marshall JD, Danaei G, Ezzati M. (2019). National and county life expectancy loss associated with particulate matter pollution in the USA: a spatiotemporal analysis, \textbf{PLOS Medicine} \href{https://doi.org/10.1371/journal.pmed.1002856}{(link)} 

    \begin{itemize}
        \item Contributed to data processing, modelling, and manuscript writing.
    \end{itemize}

% \noindent * Contributed equally to this work

% Experiences and lessons in managing water from Cape Town, Grantham Briefing Papers
     \item \textbf{Parks RM}, McLaren M, Toumi R, Rivett U. (2019). Experiences and lessons in managing water from Cape Town, \textbf{Grantham Briefing Papers} \href{https://bit.ly/2Uu9oAh}{(link)} 

    \begin{itemize}
        \item First author publication.
        \item Collaborated with experts in South Africa for policy-focused publication.
    \end{itemize}

% \subsubsection*{2018}

% (In the top 5\% of all research outputs scored by Altmetric)\\

     \item \textbf{Parks RM}, Bennett JE, Foreman KJ, Toumi R, Ezzati M. (2018). National and regional seasonal dynamics of all-cause and cause-specific mortality in the USA from 1980 to 2016, \textbf{eLife}  \href{https://doi.org/10.7554/eLife.35500}{(link)} 

    \begin{itemize}
        \item First author publication.
        \item Participated in related Reddit Ask Me Anything (AMA) interview \href{https://www.reddit.com/r/IAmA/comments/9z4703/i_am_robbie_parks_a_phd_student_looking_into_how/}{(link)}.
    \end{itemize}

% \subsubsection*{2016}

\end{enumerate}


% \begin{center} \line(1,0){450} \end{center}