\section*{Selected Peer-Reviewed Publications}

\subsection*{Published or In Press}

% \subsubsection*{2024}

\noindent Prada D, Kupsco A, Baccarelli AA, \textbf{Parks RM}. (In Press). Climate change and health: understanding mechanisms will inform
mitigation and prevention strategies. \textbf{Nature Medicine}.\href{}{ (link coming soon) \smallskip

\noindent Tuholske C, Lynch VD, Spriggs R, Ahn Y, Raymond C, Nigra AE, \textbf{Parks RM}. (2024). Hazardous heat exposure among incarcerated people in the United States. \textbf{Nature Sustainability}.\href{https://www.nature.com/articles/s41893-024-01293-y}{ (link)}\smallskip

\noindent Ahn Y, Tuholske C*, \textbf{Parks RM}*. (2024). Comparing Approximated Heat Stress Measures Across the United States. \textbf{GeoHealth}.\href{https://agupubs.onlinelibrary.wiley.com/doi/10.1029/2023GH000923}{ (link)}

\subsubsection*{2023}

USGCRP, 2023: Fifth National Climate Assessment. Crimmins, A.R., C.W. Avery, D.R. Easterling, K.E. Kunkel, B.C. Stewart, and T.K. Maycock, Eds. U.S. Global Change Research Program, Washington, DC, USA. (Technical Contributor to Chapter 14: Air Quality) \smallskip

\noindent \textbf{Parks RM}, Rowland ST, Do V, Boehme AK, Dominici F, Hart CL, Kioumourtzoglou MA. (2023). The association between temperature and alcohol- and substance-related disorder hospital visits in New York State. \textbf{Communications Medicine}. \href{https://www.nature.com/articles/s43856-023-00346-1}{(link)}\smallskip

\noindent \textbf{Parks RM}, Kontis V, Anderson GB, Baldwin JW, Danaei G, Toumi R, Dominici F, Ezzati M, Kioumourtzoglou MA. (2023). Short-term excess mortality following tropical cyclones in the United States. \textbf{Science Advances}. \href{https://www.science.org/doi/10.1126/sciadv.adg6633}{(link)} \href{https://www.science.org/toc/sciadv/9/33}{(cover art)}\smallskip

\noindent Nunez Y, Balalian A, \textbf{Parks RM}, He M, Hansen J, Raaschou-Nielsen O, Ketzel M, Khan J, Brandt J, Vermeulen R, Peters S, Goldsmith J, Re DB, Weisskopf MG, Kioumourtzoglou MA. (2023). Exploring Relevant Time Windows in the Association Between PM2.5 Exposure and Amyotrophic Lateral Sclerosis: A Case-Control Study in Denmark . \textbf{American Journal of Epidemiology}. \href{https://academic.oup.com/aje/advance-article-abstract/doi/10.1093/aje/kwad099/7135818?redirectedFrom=fulltext&login=false}{(link)}\smallskip

\noindent Casey JA, \textbf{Parks RM}, Bruckner T, Gemmill A, Catalano R. (2023). Excess Injury Mortality in Washington State During the 2021 Heat Wave. \textbf{American Journal of Public Health}. \href{https://ajph.aphapublications.org/doi/abs/10.2105/AJPH.2023.307269}{(link)}\smallskip

\noindent Flaxman S, Whittaker C, Semenova E, Rashid T, \textbf{Parks RM}, Blenkinsop A, Unwin HJT, Mishra S, Bhatt S, Gurdasani D, Ratmann O. (2023). Assessment of COVID-19 as the Underlying Cause of Death Among Children and Young People Aged 0 to 19 Years in the US. \textbf{JAMA Network Open}. \href{https://jamanetwork.com/journals/jamanetworkopen/fullarticle/2800816}{(link)}

\subsubsection*{2022}

\noindent \textbf{Parks RM}, Guinto RR. (2022). Invited Perspective: Uncovering the Hidden Burden of Tropical Cyclones on Public Health Locally and Worldwide. \textbf{Environmental Health Perspectives}. \href{https://ehp.niehs.nih.gov/doi/10.1289/EHP12241}{(link)} \href{https://ehp.niehs.nih.gov/curated-collections/eds-choice-2022}{(Editors' choice)}  \smallskip

\noindent Kepp KP, Bjork JP, Kontis V, \textbf{Parks RM}, Baek KT, Lallukka T. (2022). Estimates of excess mortality for the five Nordic countries during the COVID-19 pandemic 2020-2021, \textbf{International Journal of Epidemiology} \href{https://academic.oup.com/ije/advance-article/doi/10.1093/ije/dyac204/6798817#379089278}{(link)} \smallskip

\noindent \textbf{Parks RM}, Nunez Y, Balalian A,  Gibson EA, Hansen J, Raaschou-Nielsen O, Ketzel M, Khan J, Brandt J, Vermeulen R, Peters S, Goldsmith J, Re DB, Weisskopf MG, Kioumourtzoglou MA. (2022). Long-term traffic-related air pollutant exposure and amyotrophic lateral sclerosis diagnosis in Denmark: A Bayesian hierarchical analysis. \textbf{Epidemiology}. \href{https://journals.lww.com/epidem/Abstract/9900/Long_term_traffic_related_air_pollutant_exposure.55.aspx}{(link)} \smallskip

\noindent Elser H,* Rowland ST,* Tartof SY, \textbf{Parks RM}, Bruxvoort K, Morello-Frosch R, Robinson SC, Pressman A, Wei RX, Casey JA (2022). Ambient temperature and risk of urinary tract infection in California: A time-stratified case-crossover study using electronic health records. \textbf{Environment International} \href{https://www.sciencedirect.com/science/article/pii/S0160412022002306}{(link)} \smallskip

\noindent \textbf{Parks RM}, Benavides J, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Ezzati M, Kioumourtzoglou MA. (2022). Association of Tropical Cyclones With County-Level Mortality in the US. \textbf{JAMA} \href{https://jamanetwork.com/journals/jama/fullarticle/2789661}{(link)} \href{https://jamanetwork.com/journals/jama/fullarticle/2789676}{(editorial)} \smallskip

\noindent Kontis V, Bennett JE, \textbf{Parks RM}, Rashid T, Pearson-Stuttard J, Asaria P, Zhou B, Guillot M, Mathers CD, Khang Y, McKee M, Ezzati M. (2022). Lessons learned and lessons missed: Impact of the Covid-19 pandemic on all-cause mortality in 40 industrialised countries prior to mass vaccination, \textbf{Wellcome Open Research} \href{https://wellcomeopenresearch.org/articles/6-279/v2}{(link)} %\smallskip

% \noindent * Contributed equally to this work

\newpage

\section*{Selected Publications (Continued)}

\subsubsection*{2021}

\noindent Nethery RC, Katz-Christy N, Kioumourtzoglou MA, \textbf{Parks RM}, Schumacher A, Anderson GB. (2021). Causal predictive models for forecasting health impacts of impending tropical cyclones, \textbf{Biostatistics} \href{https://academic.oup.com/biostatistics/advance-article/doi/10.1093/biostatistics/kxab047/6485226?guestAccessKey=378fb8f6-102d-4b21-a93d-b0a01353c19f#}{(link)} \smallskip

\noindent Bock J, Srivastava P, Jessel S, Klopp JM, \textbf{Parks RM}. (2021). Heat vulnerability in New York City during COVID-19: A review of policies, tools and pilot survey results, \textbf{Journal of Extreme Events} \href{https://www.worldscientific.com/doi/10.1142/S2345737621500159}{(link)} \smallskip

\noindent Kruczkiewicz A, Klopp J, Fisher J, Mason S, McClain S, Sheekh NM, Moss R, \textbf{Parks RM}, Braneon C. (2021).\\Compound risks and complex emergencies require new approaches to preparedness, \textbf{PNAS} \href{https://www.pnas.org/content/118/19/e2106795118}{(link)} \smallskip

\noindent Rowland S, \textbf{Parks RM}, Boehme AK, Goldsmith J, Rush J, Just AC, Kioumourtzoglou MA. (2021). The Association Between Ambient Temperature Variability and Myocardial Infarction: An Examination of Different Variability Metrics, \textbf{Environmental Research} \href{https://www.sciencedirect.com/science/article/pii/S0013935121005016}{(link)} \smallskip

\noindent Elser H, \textbf{Parks RM}, Moghavem N, Bozinov B, Henderson VW, Rehkopf DH, Casey JA. (2021). Anomalously warm weather and acute care visits in patients with multiple sclerosis: A retrospective study of privately insured individuals in the U.S., \textbf{PLoS Medicine} \href{https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1003580}{(link)} \smallskip

\noindent \textbf{Parks RM}, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Kioumourtzoglou MA. (2021). Tropical cyclone exposure is associated with increased hospitalization rates in older adults, \textbf{Nature Communications} \href{https://www.nature.com/articles/s41467-021-21777-1}{(link)} \smallskip

\noindent deSouza P, Braun D, \textbf{Parks RM}, Schwartz J, Dominici F, Kioumourtzoglou MA. (2021). Nationwide Study of Short-Term Exposure to Fine Particulate Matter and Cardiovascular Hospitalizations among Medicaid Enrollees, \textbf{Epidemiology} \href{https://journals.lww.com/epidem/Abstract/2021/01000/Nationwide_Study_of_Short_term_Exposure_to_Fine.2.aspx}{(link)}

\subsubsection*{2020}

\noindent Kontis V, Bennett JE, Rashid T, \textbf{Parks RM}, Pearson-Stuttard J, Guillot M, Asaria P, Zhou B, Battaglini M, Corsetti G, McKee M, Di Cesare M, Mathers C, Ezzati M. (2020). Magnitude, demographics and dynamics of the effect of the first wave of the COVID-19 pandemic on all-cause mortality in 21 industrialized countries, \textbf{Nature Medicine} \href{https://doi.org/10.1038/s41591-020-1112-0}{(link)} \smallskip

\noindent \textbf{Parks RM}, Thalheimer L. (2020). The hidden burden of pandemics, climate change and migration on mental health, \textbf{UN International Organization for Migration (IOM) thematic series on health} \href{https://environmentalmigration.iom.int/blogs/hidden-burden-pandemics-climate-change-and-migration-mental-health}{(link)} \smallskip

\noindent Kontis V, Bennett JE, \textbf{Parks RM}, Rashid T, Pearson-Stuttard J, Asaria P, Guillot M, Blangiardo M, Ezzati M. (2020). Age- and sex-specific total mortality impacts of the early weeks of the Covid-19 pandemic in England and Wales: Application of a Bayesian model ensemble to mortality statistics, \textbf{MedrXiv} \href{https://www.medrxiv.org/content/10.1101/2020.05.20.20107680v1}{(link)} \smallskip

\noindent \textbf{Parks RM}, McLaren M, Rivett U, Thomson M. (2020). Vital signs: health security in South Africa. Chapter 5: climate, drought, food and health, \textbf{Brenthurst Foundation, Oppenheimer \& Sons} \href{https://www.thebrenthurstfoundation.org/downloads/vital-signs-ebook-pdf.pdf}{(link)} \smallskip

\noindent \textbf{Parks RM}, Bennett JE, Tamura-Wicks H, Kontis V, Toumi R, Ezzati M. (2020). Anomalously warm temperatures are associated with increased injury deaths, \textbf{Nature Medicine} \href{https://www.nature.com/articles/s41591-019-0721-y}{(link)} \href{https://www.nature.com/articles/s41591-019-0728-4}{(editorial)}
% (In the top 1\% of all research outputs scored by Altmetric)\\

% \newpage

% % HEADER 
% \input{sections/header}

% \section*{Selected Publications (Continued)}

\subsubsection*{2019}

\noindent Bennett JE*, Tamura-Wicks H*, \textbf{Parks RM}, Burnett RT, Pope CA III, Bechle MJ, Marshall JD, Danaei G, Ezzati M. (2019). National and county life expectancy loss associated with particulate matter pollution in the USA: a spatiotemporal analysis, \textbf{PLoS Medicine} \href{https://doi.org/10.1371/journal.pmed.1002856}{(link)} \smallskip

\noindent * Contributed equally to this work

\noindent \textbf{Parks RM}, McLaren M, Toumi R, Rivett U. (2019). Experiences and lessons in managing water from Cape Town, \textbf{Grantham Briefing Papers} \href{https://bit.ly/2Uu9oAh}{(link)} \smallskip

\subsubsection*{2018}

\noindent \textbf{Parks RM}, Bennett JE, Foreman KJ, Toumi R, Ezzati M. (2018). National and regional seasonal dynamics of all-cause and cause-specific mortality in the USA from 1980 to 2016, \textbf{eLife}  \href{https://doi.org/10.7554/eLife.35500}{(link)} \smallskip
% (In the top 5\% of all research outputs scored by Altmetric)\\

\subsubsection*{2016}

\noindent \textbf{Parks RM}. (2016). Weather, climate and health, \textbf{Weather} \href{https://doi.org/10.1002/wea.2752}{(link)} \smallskip

% \begin{center} \line(1,0){450} \end{center}